Neural Neural Textures Make Sim2Real Consistent

### 2022-06-24 CORL/appendix.tex
Added lTR everywhere we say w/o lUC

	In this section we detail the training procedures used to create results in section \ref{sec:results} from Triton, CycleGAN, CUT,
		TRITON w/o $\lUC$ (aka TRITON with neither unprojection consistency loss nor texture reality loss), and
		TRITON w/o $\psi, \lUC$ (aka TRITON without textures, and therefore also without unprojection consistency loss or texture reality loss).

@@

	Like in \cite{surgical_video_translation}, we use three Adam optimizers: two for the translation module's encoders and decoders, and another for the neural texture.
	For the translation module's optimizers, we use learning rate $\num{1e-4}$, and for the neural neural texture we use learning rate $\num{1e-3}$. 
	Every 100,000 iterations all learning rates are halved.
	During evaluation, we render the neural neural texture onto a raster grid of pixels. Because the neural neural texture has a 2d manifold, it can be closely approximated by an RGB image. Using this method lets us avoid evlauating $\psi$'s fourier feature network on every frame by using a raster image as a lookup table. This decreases video memory usage and speeds up calulations during inference.

	\subsubsection{TRITON w/o $\lUC$}
	\label{par:triton_without_luc}
	This ablation is also known as ``Texture-Only'' TRITON, because it has a learnable texture $\psi$ but no consistency losses.
	Its trained the same way that we train TRITON normally as discussed above in \ref{par:triton}, except the surface consistency losses $\lUC$ and $\lTR$ are omitted.
	Effectively, it performs better than MUNIT-like TRITON (aka TRITON w/o $\psi, \lUC$, discussed in \ref{par:munit_triton})
	% It still has a learnable texture $\psi$ though, which is allowed to change however it likes.

	\subsubsection{TRITON w/o $\psi, \lUC$}
	\label{par:munit_triton}
	This ablation is very similar to MUNIT, as TRITON is based on MUNIT and this ablation has neither learnable texture nor consistency losses.
	Like in subsection \ref{par:triton_without_luc}, this ablation shares the same training procedures as TRITON.

>>>>

	In this section we detail the training procedures used to create results in section \ref{sec:results} from Triton, CycleGAN, CUT,
		TRITON w/o $\lUC,\lTR$ (aka TRITON with neither unprojection consistency loss nor texture reality loss), and
		TRITON w/o $\psi, \lUC,\lTR$ (aka TRITON without textures, and therefore also without unprojection consistency loss or texture reality loss).

@@

	Like in \cite{surgical_video_translation}, we use three Adam optimizers: two for the translation module's encoders and decoders, and another for the neural texture.
	For the translation module's optimizers, we use learning rate $\num{1e-4}$, and for the neural neural texture we use learning rate $\num{1e-3}$. 
	Every 100,000 iterations all learning rates are halved.

	During evaluation, we render the neural neural texture onto a raster grid of pixels. Because the neural neural texture has a 2d manifold, it can be closely approximated by an RGB image. Using this method lets us avoid evlauating $\psi$'s fourier feature network on every frame by using a raster image as a lookup table. This decreases video memory usage and speeds up calulations during inference.

	\subsubsection{TRITON w/o $\lUC,\lTR$}
	\label{par:triton_without_luc}
	This ablation is also known as ``Texture-Only'' TRITON, because it has a learnable texture $\psi$ but no consistency losses.
	Its trained the same way that we train TRITON normally as discussed above in \ref{par:triton}, except the surface consistency losses $\lUC$ and $\lTR$ are omitted.
	Effectively, it performs better than MUNIT-like TRITON (aka TRITON w/o $\psi, \lUC,\lTR$, discussed in \ref{par:munit_triton})
	% It still has a learnable texture $\psi$ though, which is allowed to change however it likes.

	\subsubsection{TRITON w/o $\psi, \lUC,\lTR$}
	\label{par:munit_triton}
	This ablation is very similar to MUNIT, as TRITON is based on MUNIT and this ablation has neither learnable texture nor consistency losses.
	Like in subsection \ref{par:triton_without_luc}, this ablation shares the same training procedures as TRITON.

### 2022-06-24 CORL/example.tex
Added optimizer details
Added lTR everywhere we say w/o lUC

\usepackage[preprint]{corl_2022} % Use this for the initial submission.
% \usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{multirow}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{array, booktabs, ragged2e}
\usepackage{comment}

@@

\begin{figure}[tbhp]
    \centering
    \vspace{-3pt}
    \includegraphics[width=.95\textwidth]{../images/sim2real_res.pdf}
    \vspace{-5pt}
    \caption{Evaluation results of sim2real robot learning. We compare TRITON against two baselines and one TRITON variant w/o $\ell_{UC}$ across 3 different input image resolutions. TRITON outperforms CycleGAN~\cite{cyclegan} and CUT~\cite{cut} consistently across (a) all resolutions and (b) unseen viewpoints. Results in (a) are from Seen setting only. Results in (b) are from 336x336 resolution. }
    \label{fig:sim2real}
    \vspace{-3pt}
\end{figure}

\textbf{Results} Figure~\ref{fig:sim2real} shows the evaluation results of the sim2real transfer. Both Seen and Unseen evaluations show that TRITON outperforms baselines consistently. In Figure~\ref{fig:sim2real}(a), we find that TRITON continuously improves from low to high resolutions due to its ability to generate more photo-realistic images compared to the baselines.
%This is because in low resolution (eg. $84\times 84$), the details in images are not important, whereas in high resolution ($336\times 336$), artifacts from imperfect translator are clearer and may harm policy learning.
From Figure~\ref{fig:sim2real}(b), we confirm that TRITON outperforms the others also in the Unseen setting, showing that TRITON learns image translations that are generalizable to new viewpoints while others are limited.
In the comparison against TRITON w/o $\ell_{UC}$, TRITON outperforms this variant consistently except the lowest resolution. This again shows the effectiveness of $\ell_{UC}$ to generate photo-realistic images, and such high quality images are important in higher resolutions for sim2real transfer.

>>>>

\usepackage[preprint]{corl_2022} % Use this for the initial submission.
% \usepackage[final]{corl_2022} % Uncomment for the camera-ready ``final'' version.
\usepackage{graphicx}
\usepackage{float}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{multicol}
\usepackage{multirow}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{array, booktabs, ragged2e}
\usepackage{comment}
\usepackage{siunitx}

@@

\begin{figure}[tbhp]
    \centering
    \vspace{-3pt}
    \includegraphics[width=.95\textwidth]{../images/sim2real_res.pdf}
    \vspace{-5pt}
    \caption{Evaluation results of sim2real robot learning. We compare TRITON against two baselines and one TRITON variant w/o $\psi,\ell_{UC},\lTR$ across 3 different input image resolutions. TRITON outperforms CycleGAN~\cite{cyclegan} and CUT~\cite{cut} consistently across (a) all resolutions and (b) unseen viewpoints. Results in (a) are from Seen setting only. Results in (b) are from 336x336 resolution. }
    \label{fig:sim2real}
    \vspace{-3pt}
\end{figure}

\textbf{Results} Figure~\ref{fig:sim2real} shows the evaluation results of the sim2real transfer. Both Seen and Unseen evaluations show that TRITON outperforms baselines consistently. In Figure~\ref{fig:sim2real}(a), we find that TRITON continuously improves from low to high resolutions due to its ability to generate more photo-realistic images compared to the baselines.
%This is because in low resolution (eg. $84\times 84$), the details in images are not important, whereas in high resolution ($336\times 336$), artifacts from imperfect translator are clearer and may harm policy learning.
From Figure~\ref{fig:sim2real}(b), we confirm that TRITON outperforms the others also in the Unseen setting, showing that TRITON learns image translations that are generalizable to new viewpoints while others are limited.
In the comparison against TRITON w/o $\psi,\ell_{UC},\lTR$, TRITON outperforms this variant consistently except the lowest resolution. This again shows the effectiveness of $\psi$, $\ell_{UC}$ and $\lTR$ to generate photo-realistic images, and such high quality images are important in higher resolutions for sim2real transfer.
